Capstone Movielens Report

### 2025-12-10 reports/capstone-movielens.site/05.appendix.Rmd
Micro fix for function description: loess_de.

#### [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L69) Function {#func.loess_de}
\

>>>>

#### [loess_de](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGYD-effect.functions.R#L71) Function {#func.loess_de}
\
